### 2021-10-23 docs/manuscript/manuscript.tex
Improve captions
Improve Fig. 6 caption
Include S1 Appendix in main text
Improve S3 Fig caption

\begin{figure}[!h]
%  \includegraphics[width=\textwidth]{figures/results/Fig6}
 \caption{\bf Relationship between Abundance and robustness and complexity
 index.} (A) Abundance vs. Robustness. The robustness of each topology was
 calculated as the ratio of perturbations in which the fitness was greater or
 equal to 0.95 with respect to the total of perturbations performed.
 (B) Abundance vs. Complexity index. Each point in the plot represents one of
 the 714 network topologies. More complex topologies tend to be less abundant
 than simple topologies
 ($r_S = -0.316653$, $\text{p-value} = 2.25161\times10^{-18}$).
 \label{fig:ab-rob}
\end{figure}

On the other hand, analysis of the average vertex degree seems to be indicative
that network topologies are likely to withstand numerous topological
modifications (approximately 4) without significant loss in their ability to
generate a striped pattern of gene expression, representing a high fitness
solution to the prescribed task. The average complexity index of network
topologies was 39.2435 ($\pm 11.6768$) and was found to be negatively
correlated with the abundance ($r_S = -0.316653$, $\text{p-value} =
2.25161\times10^{-18}$) (Fig~\ref{fig:ab-rob}B).
Additionally, the average path length seems
to suggest that the evolutionary landscape could be easily traversed by
most network topologies without incurring in significant fitness loss as long
as mutational changes results in moves between adjacent neighbors across
the metagraph (Table~\ref{table1}). It is interesting to note that,
although the examined GRNs seem to exhibit, on average, a high robustness to
topological/parameter changes, they generally show a rather high sensitivity to
variation in the size of the morphogenetic field. For instance, we found that
when the size of the morphogenetic field was fixed at 10, 20, 40 and 50 cells
only 4.66\%, 56.82\%, 56.14\% and 41.05\%, respectively, of the examined
GRNs showed a fitness greater than 0.9 (\nameref{S3_Fig}B).

@@

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Response of GRNs to changes in morphogenetic field size.}
(A) Morphogen gradients of fields with 10, 20, 40 and 50 cells. (B) Fitness of the
GRNs by topology in each one of the morphogenetic fields. (C) Principal Component
Analysis of fitness by morphogenetic field size. Although principal components
separate GRNs in clusters, not all the GRNs with the same topology are located in the
same group. (D) Average fitness of GRNs evolved in different morphogenetic
field sizes.

>>>>

\begin{figure}[!h]
%  \includegraphics[width=\textwidth]{figures/results/Fig6}
 \caption{\bf Relationship between the abundance of topologies with
 robustness and complexity index.}
 (A) Abundance vs. Robustness. The robustness of each topology was
 calculated as the ratio of perturbations in which the fitness was greater or
 equal to 0.95 with respect to the total of perturbations performed.
 (B) Abundance vs. Complexity index. Each point in the plot represents one of
 the 714 network topologies. More complex topologies tend to be less abundant
 than simple topologies
 ($r_S = -0.316653$, $\text{p-value} = 2.25161\times10^{-18}$).
 \label{fig:ab-rob}
\end{figure}

On the other hand, analysis of the average vertex degree seems to be indicative
that network topologies are likely to withstand numerous topological
modifications (approximately 4) without significant loss in their ability to
generate a striped pattern of gene expression, representing a high fitness
solution to the prescribed task. The average complexity index of network
topologies was 39.2435 ($\pm 11.6768$) and was found to be negatively
correlated with the abundance ($r_S = -0.316653$, $\text{p-value} =
2.25161\times10^{-18}$) (Fig~\ref{fig:ab-rob}B).
Additionally, the average path length seems
to suggest that the evolutionary landscape could be easily traversed by
most network topologies without incurring in significant fitness loss as long
as mutational changes results in moves between adjacent neighbors across
the metagraph (Table~\ref{table1}). It is interesting to note that,
although the examined GRNs seem to exhibit, on average, a high robustness to
topological/parameter changes, they generally show a rather high sensitivity to
variation in the size of the morphogenetic field. For instance, we found that
when the size of the morphogenetic field was fixed at 10, 20, 40 and 50 cells
only 4.66\%, 56.82\%, 56.14\% and 41.05\%, respectively, of the examined
GRNs showed a fitness greater than 0.9 (\nameref{S3_Fig}B). In addition to
robustness, we wanted to investigate which of the GRNs could still produce
a striped pattern in absence of diffusion, as it has been shown that some
networks can work without diffusion involved \cite{Schaerli2018}. We found
that out of 2061 GRNs, 404 were diffusion independent, many of them
presenting the I3-FFL (see \nameref{S1_Appendix}).

@@

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Response of GRNs to changes in morphogenetic field size.}
(A) Morphogen gradients of fields with 10, 20, 40 and 50 cells. These
morphogen gradients were set up so that the morphogen concentration in the
first cell and in the last cell were constant and only one
morphogen gradient was considered at a time depending on the number of
cells in the morphogenetic field. (B) Fitness of the
GRNs by topology in each one of the morphogenetic fields. (C) Principal Component
Analysis of fitness by morphogenetic field size. Although principal components
separate GRNs in clusters, not all the GRNs with the same topology are located in the
same group. (D) Average fitness of GRNs evolved in different morphogenetic
field sizes.
